---
title: "postAAR: Vignette"
author: "Nils Müller-Scheeßel"
date: "May 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction
## built postAAR_subroutine.so for your system

R CMD SHLIB postAAR_subroutine.f

## load libraries data.table and spatstat
library(data.table)
library(spatstat)

## Simulatie point patterns
set.seed(20)
pp<-sim_rect(0,200,200,2,5,0.4,70,500,3,4)
plot(pp$points)

## add the simulated houses to the plot

plot(pp$lines, add=TRUE)

## extract the coordinates

pp_coords<-coords(pp$points)
str(pp_coords)

## Then fuel it into find_rect with minimum distance = 2, maximum distance = 5 and tolerance = 1

pa<-find_rect(pp_coords$x,pp_coords$y,2,5,1)

## plot the rectangles
plot(pa$lines)

## plot the points
plot(pa$points)


## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
